Why Donors Donate: Disentangling Organizational and Structural Heuristics for International Philanthropy

### 2023-10-27 manuscript/manuscript.qmd
Add a few placeholders

# Methods

## Conjoint analysis

@@

@@

## Modeling

@@

@@

# Conclusion
Over the last two decades, governments globally have systematically controlled and repressed NGOs using both violent tactics and administrative means over the last three decades -- a phenomenon known as `closing' or `shrinking' civic space. This trend of closing civic space has important implications for local and international NGOs as well as donors. Recent research has analyzed the impact of this crackdown on public or official aid donors. However, we know relatively little about how state repression of NGOs affects the preferences of foreign private donors. The responses of elite donors and foundations to government crackdown on civil society organizations remains a ripe area for research. Unlike state donors, individual and elite donors may not necessarily withdraw or reduce support for NGOs facing harassment abroad. This is important because private philanthropy towards organizations working in international affairs continues to grow despite inflation -- from 2021 to 2022, individual giving to nonprofits in international affairs grew by over 10.9% in the US [@GivingUSA:2023].

>>>>

# Research design

TODO: Cite @ChaudhryHeiss:2022

We use an experiment...

## Conjoint research design

@@

TODO: More on conjoint stuff

Before launching the survey experiment, in an effort to avoid issues with p-hacking and cherry-picking results, we preregistered a series of confirmatory hypotehses at the Open Science Framework, and our preregistration protocol is available at URL. Appendix contains blah. Analysis fully reproducible using code and data available at BLAH

@@

## Modeling and estimation

@@

Marginal means and marginalization across a balanced reference grid

@@

# Conclusion

Over the last two decades, governments globally have systematically controlled and repressed NGOs using both violent tactics and administrative means over the last three decades -- a phenomenon known as `closing' or `shrinking' civic space. This trend of closing civic space has important implications for local and international NGOs as well as donors. Recent research has analyzed the impact of this crackdown on public or official aid donors. However, we know relatively little about how state repression of NGOs affects the preferences of foreign private donors. The responses of elite donors and foundations to government crackdown on civil society organizations remains a ripe area for research. Unlike state donors, individual and elite donors may not necessarily withdraw or reduce support for NGOs facing harassment abroad. This is important because private philanthropy towards organizations working in international affairs continues to grow despite inflation -- from 2021 to 2022, individual giving to nonprofits in international affairs grew by over 10.9% in the US [@GivingUSA:2023].
